Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-18 bdcloud_paper/latex/paper.tex
Created evaluation section

We determine the number of pets $N_p$ each customer has by sampling from a uniform distribution of integers. We then sample the number of dogs $N_d$ as a uniform distribution between 0 and $N_p$.  The remaining number of pets are assigned to be cats.

@@

\section{Example Analysis of Generated Data}
Using data for 10 stores, 10,000 customers, and five years of transactions generated from the model, we performed two example analyses in support of a fictional advertising campaign. The analyses were designed to be realistic and driven by real-world business concerns.  Due to limited advertising budgets, businesses need to decide who to target and what sort of advertisements are likely to be effective for each type of customer.  We analyzed data generated from the model to determine where the advertising campaigns should be targeted geographically and identify customer purchasing profiles.

@@

\section{Scaling of Data Size and Run Time}
BigPetStore aims to scale from a local desktop to a large cluster. As a result, we benchmarked the generation of data on a laptop with a 2 GHz Intel Core i7 CPU, 8 GB of RAM, and a 256 GB SSD using the Python implementation with a single thread. Using the test setup, between 1,500 and 2,000 transactions can be generated per second (Table~\ref{tab:benchmarks}). As the customers' transaction simulations are independent of one another, the transaction generation can easily be parallelized so that 1,500-2,000 transactions can be generated per thread per second.

>>>>

We determine the number of pets $N_p$ each customer has by sampling from a discrete uniform distribution of integers. We then sample the number of dogs $N_d$ as a discrete uniform distribution of integers between 0 and $N_p$.  The remaining number of pets are assigned to be cats.

@@

\section{Evaluation of the Model}

\textcolor{red}{intro paragraph}

\subsection{Example Analysis of Generated Data}
Using data for 10 stores, 10,000 customers, and five years of transactions generated from the model, we performed two example analyses in support of a fictional advertising campaign. The analyses were designed to be realistic and driven by real-world business concerns.  Due to limited advertising budgets, businesses need to decide who to target and what sort of advertisements are likely to be effective for each type of customer.  We analyzed data generated from the model to determine where the advertising campaigns should be targeted geographically and identify customer purchasing profiles.

@@

\subsection{Scaling of Data Size and Run Time}
BigPetStore aims to scale from a local desktop to a large cluster. As a result, we benchmarked the generation of data on a laptop with a 2 GHz Intel Core i7 CPU, 8 GB of RAM, and a 256 GB SSD using the Python implementation with a single thread. Using the test setup, between 1,500 and 2,000 transactions can be generated per second (Table~\ref{tab:benchmarks}). As the customers' transaction simulations are independent of one another, the transaction generation can easily be parallelized so that 1,500-2,000 transactions can be generated per thread per second.
